---
title: "PRECISE Value Plots"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(here)
library(tidyverse)
library(scales)
library(plotly)
```

```{r}
source(here("src", "make_inputs.R")) # functions to generate starting data frames
source(here("src", "precise_value_base_values.R")) # initialize values
source(here("src", "precise_value_r_model.R")) # build model
source(here("src", "precise_value_psa.R")) # holds function for PSA
source(here("R", "precisevalue.R"))
return_list <- precise_value(start_age = 55, test_rate = 0.1,
                             screen_dur = 5, t_horizon = 20,
                             p_new_rx = 0.005)
outcomes <- return_list[[1]]
total <- return_list[[2]]
```

Inputs {.sidebar data-width=250}
-----------------------------------------------------------------------

```{r}
precisevalueUI("input_parameters")
```


```{r}
# Placeholder to display input parameters
# Set demographic parameters
#n <- 320000  #population size

# racial demographics from overall US demographics
p_a <- 0.06 #percentage of population Asian
p_b <- 0.13 #percentage of population Black
p_l <- 0.18 #percentage of population Latinx
p_w <- 0.60 #percentage of population White
p_o <- 0.03 #percentage of population other race

# probability of plan modification based on alert / no alert
p_change_alert <- 0.9
p_change_no_alert <- 0.1

# qalys and costs of changing pgx
qaly_change_clo <- 0.05
cost_change_clo <- 1265
qaly_change_sim <- 0  # simvastatin no longer included
cost_change_sim <- 0  # as of 6/22
qaly_change_war <- 0.01
cost_change_war <- -50

# time horizon (years)
# t_horizon <- 20

# costs associated with alert
# start_up_cost <- 4000
# maint_cost <- 100

# testing and medication use patterns
# screen_dur <- 5 # years of screening
# p_new_rx <- 0.005 # annual probability of a new rx for one of the included drugs
# test_rate <- 0.1 # annual probability of testing for patients in the selected age range
# start_age <- 55 # age at start of screening
```

Column {data-width=750}
-----------------------------------------------------------------------

### Summary

```{r}
renderText(paste0("ICER = ", round((sum(total$alert_cost) - sum(total$no_alert_cost))/(sum(total$alert_qaly) - sum(total$no_alert_qaly)),2)))
```

ICER = `r round((sum(total$alert_cost) - sum(total$no_alert_cost))/(sum(total$alert_qaly) - sum(total$no_alert_qaly)),2)`

Cost per alert = `r round((sum(total$alert_cost) - sum(total$no_alert_cost))/sum(total$alert_n),2)`

N alert = `r sum(total$alert_n)`

Admin cost per alert = `r round(sum(outcomes$alert_cost)/sum(total$alert_n),2)`

Change cost per alert = `r round((sum(total$alert_cost) - sum(outcomes$alert_cost) - sum(total$no_alert_cost))/sum(total$alert_n),2)`

```{r, include = FALSE}
cat(paste0("ICER = ", round((sum(total$alert_cost) - sum(total$no_alert_cost))/(sum(total$alert_qaly) - sum(total$no_alert_qaly)),2),
           "\nCost per alert = ", round((sum(total$alert_cost) - sum(total$no_alert_cost))/sum(total$alert_n),2),
           "\nn alert = ",sum(total$alert_n),
           "\nadmin cost per alert = ", round(sum(outcomes$alert_cost)/sum(total$alert_n),2),
           "\nreg change cost per alert = ", round((sum(total$alert_cost) - sum(outcomes$alert_cost) - 
                                                      sum(total$no_alert_cost))/sum(total$alert_n),2)))
```

### PSA

```{r}
#source(here("src", "precise_value_psa.R"))
renderPlotly({
  psa(input$pop_size)
})
#ggplotly(psa_plot)
```

### OWSA

```{r}
source(here("src", "precise_value_owsa.R"))
ggplotly(owsa_plot)
```
